---
title: "Wildlife monitoring report"
subtitle: "GitHub and Quarto workshop"
author: "Your name"
date: today
format:
  html:
    toc: true
    embed-resources: true
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: false
  message: false
---

## About this report

This short report demonstrates how Quarto combines text, R code, results,
tables and figures in one reproducible document.

::: {.callout-tip}
## Your first task

Change the author in the YAML header and replace this box with two or three
sentences about your own research interests.
:::

## Example data

For this exercise, we will create a small fictional camera-trap dataset. Each
row represents one monitoring site.

```{r}
#| label: create-data

observations <- data.frame(
  site = paste("Site", LETTERS[1:6]),
  habitat = c("Forest", "Forest", "Wetland", "Grassland", "Wetland", "Forest"),
  survey_nights = c(10, 12, 8, 10, 9, 11),
  detections = c(12, 7, 15, 4, 9, 13)
)

observations$detections_per_night <-
  observations$detections / observations$survey_nights

observations
```

## A reproducible result

The survey recorded **`r sum(observations$detections)` detections** across
**`r sum(observations$survey_nights)` camera-trap nights**. The mean number of
detections per site was **`r round(mean(observations$detections), 1)`**.

The numbers in that sentence are generated directly from the data. If the data
change, the sentence will update when the document is rendered again.

## Figure

```{r}
#| label: detections-figure
#| fig-cap: "Fictional wildlife detections recorded at six monitoring sites."
#| fig-alt: "Bar chart comparing the number of wildlife detections across six sites."

barplot(
  height = observations$detections,
  names.arg = observations$site,
  col = "#2F6B4F",
  border = NA,
  xlab = "Monitoring site",
  ylab = "Number of detections"
)
```

## Table

```{r}
#| label: results-table

knitr::kable(
  observations,
  digits = 2,
  caption = "Example camera-trap monitoring data."
)
```

## Interpretation

In this fictional example, Site C recorded the largest number of detections.
However, the sites were not all surveyed for the same number of nights, so a
comparison of raw detections alone may be misleading.

::: {.callout-note}
## Your second task

1. Change one of the values in `detections`.
2. Render the document again and observe what changes.
3. Add one sentence interpreting `detections_per_night`.
4. Save the file, inspect the changes in the Git pane and commit them with a
   meaningful message.
:::

## Reproducibility information

This report was created with R and Quarto. The following command records the R
version and packages used to render it.

```{r}
#| label: session-information

sessionInfo()
```
